---
title: "Report template"
subtitle: "<i>Analysis report generated by INSiGENe and shall not be reproduced without approval of INSiGENe Pty Ltd</i>"
author: "Sebastian Rauschert"
title-block-banner: Background.png
format: 
  html:
    code-fold: true
    code-overflow: scroll
    code-tools: false
    toc: true
    toc-location: left
    embed-resources: true
    highlight-style: github
editor: visual
date: today
theme: 
  light: [flatly, insigene-light.scss]
  dark: [darkly, insigene-dark.scss]
bibliography: bibliography.bib
lightbox: auto
execute:
  warning: false
  error: false
  message: false
---

# Overview

This is a template for an html report provided by insigene

# Code

```{r}
library(ggplot2)
library(magrittr)
library(insigene)
iris%>%
  ggplot(aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point() +
  theme_minimal()
```

```{r}
#| include: false

theme_insigene_dark <- function() {
    theme(
    plot.background = element_rect(fill = "#000d19"),
    panel.background = element_rect(fill = "#000d19"),
    panel.grid.major.y = element_blank(), #element_line(color = "white"),
    panel.grid.major.x = element_blank(), #element_line(color = "white"),
    panel.grid.minor = element_line(color = "white"), #element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", 
                              size = 14, 
                              face = "bold"),
    plot.subtitle = element_text(color = "white", 
                                 size = 12),
    legend.background = element_rect(fill = "#000d19"),
    legend.text = element_text(color = "white",
                               size = 12),
    legend.title = element_text(color = "white",
                                size = 14),
    axis.text.y = element_text(color = "white",
                               size = 9),
    axis.text.x = element_text(color = "white",
                               size = 9),
    panel.border = ggplot2::element_blank()
    
  ) 
}


theme_insigene_light <- function() {
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_blank(), #element_line(color = "white"),
    panel.grid.major.x = element_blank(), #element_line(color = "white"),
    panel.grid.minor = element_line(color = "#000d19"), #element_blank(),
    axis.text = element_text(color = "#000d19"),
    axis.title = element_text(color = "#000d19"),
    plot.title = element_text(color = "#000d19",
                              size = 14,
                              face = "bold"),
    plot.subtitle = element_text(color = "#000d19",
                                 size = 12),
    legend.background = element_rect(fill = "white"),
    legend.text = element_text(color = "#000d19",
                               size = 12),
    legend.title = element_text(color = "#000d19",
                                size = 14),
    axis.text.y = element_text(color = "#000d19",
                               size = 9),
    axis.text.x = element_text(color = "#000d19",
                               size = 9),
    panel.border = ggplot2::element_blank()

  )
}



```

# Example for lightbox

The below header is an example how a gallery with click-through images can be created. The important parts are the `group:` and `fig-sub-cap` assignments. Without the `group`, plots will appear but not be click through.

This also includes teh `theme_insigene_dark()` and `theme_insigene_light()` for `ggplot2`. This is currently in $\beta$.

```{r}
#| lightbox:
#|   group: vln_heat
#| fig-cap: Spatial transcriptomics data from all samples; Ren et al. and TKI
#| fig-subcap:
#|    - "Plot 1"
#|    - "plot 2"
#| layout-ncol: 2

plot_list <- list(
  iris %>% 
    ggplot(aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
    geom_point(size = 3, alpha = 0.8) +
    theme_insigene_dark() +
    ggtitle("Plot 1"),
  
  iris %>%
    ggplot(aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
    geom_point(size = 3, alpha = 0.8) +
    theme_insigene_light() +
    ggtitle("Plot 2")
)

purrr::walk(plot_list, print)

```

# Citation DB

Decipher paper per [@Basto2024.05.01.591681]

# References

::: {#refs}
:::

# Session Info

<details>

<summary>Show Details</summary>

```{r}
sessionInfo()
```

</details>
