---
title: "Decipher Visualizations Tutorial"
subtitle: "<i>How to visualize Decipher outputs</i>"
author: "Edgar Basto"
title-block-banner: Background.png
format: 
  html:
    code-fold: false
    code-overflow: scroll
    code-tools: false
    toc: true
    toc-location: left
    embed-resources: true
    highlight-style: github
editor: visual
date: today
theme: 
  light: [flatly, insigene-light.scss]
  dark: [darkly, insigene-dark.scss]
bibliography: bibliography.bib
lightbox: auto
execute:
  warning: false
  error: false
  message: false
---

```{r}
#| eval: true
#| include: true
# Running this in the root of the Decipher repository
renv::restore()   # ensure reproducible library state, say yes if asked to install packages (will install from cache)
library(devtools)
load_all()
library(data.table)
set.seed(123)
```

Overview

This vignette shows how to load Decipher results and generate common visualizations: 
* volcano plots
* the prioritized Decipher map
* LR→TF heatmaps 
* sorted TF heatmaps per cluster 
* pubmed target-gene heatmaps, and 
* network plots.

0. Setup / paths

```{r}
#| eval: true
dataset_path <- "results/sample_analysis"
pre_processing_filepath <- file.path(dataset_path, "pre_processing")
reference_filepath <- file.path("reference_data")
output_data_filepath <- file.path(dataset_path, "data")
figures_folder <- "figures"
output_figures_filepath <- file.path(dataset_path, "figures")
dir.create(figures_folder, showWarnings = FALSE, recursive = TRUE)
```

1. Load Data & Pre-process for plotting

```{r}
#| eval: true
# Load saved Decipher results and run pre-processing helper
decipher_results <- safe_load(file.path(output_data_filepath, "decipher_scores_by_cluster.rds"))
decipher_pre_processed <- preProcessDecipher(decipher_results)

results_preprocessed <- list()
results_preprocessed <- add_if_not_null(results_preprocessed, "Decipher", decipher_pre_processed)

# Prepare objects used for comparison/correlation plots
results_for_correlation <- lapply(names(results_preprocessed), function(name) {
  prepareForCorrelation(name, results_preprocessed[[name]])
})
names(results_for_correlation) <- names(results_preprocessed)

decipher_results_for_comparison <- lapply(decipher_results, "renameDecipherScore")
results_for_comparison <- list()
results_for_comparison <- add_if_not_null(results_for_comparison, "Decipher", decipher_results_for_comparison)
```

2. Volcano plot of TF activity by cell-type

```{r}
#| eval: true
selected_cluster <- names(decipher_results)[1]
differentialTFActivityVolcanoPlotByCluster(
  output_data_filepath,
  selected_cluster,
  figures_folder,
  p_threshold = 0.01,
  fc_threhsold = 2.883,
  output_filename = "diff_regulong_act_volcano_plot"
)
# Output saved under figures_folder
```

3. Decipher prioritized map (heatmap of top interactions)

```{r}
#| eval: true
plotDecipherPrioritizedMap(
  dataset_path,
  top_n = 6,
  priority_receiver_cells = selected_cluster,
  dataset_name = "sample_dataset",
  width = 21,
  height = 11
)
# Note: this function may display in-session; save/export as needed.
```

4. LR → TF heatmap (TFs tied to upstream LR pairs)

```{r}
#| eval: true
plotLRTFHeatmap(
  output_data_filepath,
  selected_cluster,
  figures_folder,
  p_threshold = 0.01,
  output_name = "lr_tf_heatmap",
  n_interactions = 10,
  min_abs_decipher_score = 0.4,
  min_delta_pagoda = 2
)
```

5. Sorted TF heatmaps (per cluster)

```{r}
#| eval: true
selected_clusters <- names(decipher_results)
# load regulon deltas
file_path <- file.path(output_data_filepath, "regulon_deltas_by_cluster.rds")
regulon_deltas_by_cluster <- load_regulon_data(file_path, selected_clusters)

# Calculate a global absolute max for consistent color scales
absolute_max <- find_absolute_max_simple(regulon_deltas_by_cluster)
if (is.na(absolute_max) || absolute_max <= 0) {
  warning("Could not determine a valid absolute max deltaPagoda. Setting scale limit to 1.")
  absolute_max <- 1
}

top_n <- 15
for (cell_type in selected_clusters) {
  p <- plotClusterSortedTFHeatmap(
    selected_cluster = cell_type,
    top_n = top_n,
    deltas_by_cluster = regulon_deltas_by_cluster,
    global_max = absolute_max   # optional: fix color scale across multiple plots
  )

  file_name <- paste0("sorted_tf_deltas_", cell_type, "_", top_n, ".png")
  ggsave(file.path(figures_folder, file_name), p, width = 8, height = 3)
  file_name_csv <- paste0("sorted_tf_deltas_", cell_type, "_", top_n, ".csv")
  write.csv(p$data, file.path(figures_folder, file_name_csv), row.names = TRUE)
}
```

6. PubMed target-gene heatmaps

```{r}
#| eval: true
n_pubmed <- 40
plot_pubmed_tg_heatmaps(
  output_data_filepath,
  selected_clusters[1],
  n_pubmed
)
```

7. Network plots (sender / receiver network visualisations)

```{r}
#| eval: true
selected_clusters <- names(decipher_results)
# Example: visualize networks for a target receiver cluster (or vector of clusters)
target_clusters <- selected_clusters[3]
sender_cts <- selected_clusters

for (cl in target_clusters) {
  generate_network_plot(
    "sample_analysis",
    cl,
    output_data_filepath,
    sender_cts,
    figures_folder,
    top_interactions = NULL,
    scaling_global_sender_ligand_max = 1/1.2,
    scaling_global_decipher_score_max = 1/1.5,
    n_top_regulons = 10
  )
}
```

Session Info

<details>

<summary>Show Details</summary>

```{r}
#| eval: true
sessionInfo()
````

</details>